---
title: "Hockey sticks, rank dif, and clustering"
output: html_notebook
---

```{r setup}
#source("~/Script repository/R scripting/My_Useful_Fns.R")#02/01/2022 commit at my github https://github.com/McK-Ford/Script-repository/blob/main/R%20scripting/My_Useful_Fns.R
library(tidyverse)
library(data.table)
DIR <- "C:/Users/kayle/Box/Vertinolab/GenomicSandbox/project_cell_lines/ProSeq/PEPPRO_SE/"
MB231_pI <- read.delim(
  paste0(DIR, "MB231/QC_hg38/MB231_pause_index.bed.gz"),
  header = FALSE,
  skipNul = TRUE
  )
MCF7_pI <- read.delim(
  paste0(DIR, "MCF7/QC_hg38/MCF7_pause_index.bed.gz"),
  header = FALSE,
  skipNul = TRUE
  )
MCF10A_pI <- read.delim(
  paste0(DIR, "MCF10A/QC_hg38/MCF10A_pause_index.bed.gz"),
  header = FALSE,
  skipNul = TRUE
  )
SUM159_pI <- read.delim(
  paste0(DIR, "SUM159/QC_hg38/SUM159_pause_index.bed.gz"),
  header = FALSE,
  skipNul = TRUE
  )
T47D_pI <- read.delim(
  paste0(DIR, "T47D/QC_hg38/T47D_pause_index.bed.gz"),
  header = FALSE,
  skipNul = TRUE
  )
```
skipNul - if do not provide this parameter, SUM and T47D fail with a 'line 1
appears to contain embedded nullsWarning'. This appears to be some kind of
encoding issue, but the data in R agrees with the data in excel once you add
skipNul, so it's not really worth messing with further.


Did we decide for sure what our filtering threshold would be? Talked with Paula. Greater than 95% confidence interval based on the log of the pI? 3 standard deviations is 99.7% of the data, given how few outliers we have on an arbitrary definition of such I'd prefer that. Or as we discussed with Paula, we could just do greater than 1K as threshold.
```{r}
tab_lst <- list(MB231 = MB231_pI,
               MCF10A = MCF10A_pI, 
               MCF7 = MCF7_pI,
               SUM159 = SUM159_pI,
               T47D = T47D_pI)
for (i in seq_along(tab_lst)) {
  colnames(tab_lst[[i]]) = c("chrom", "start", "end", "symbol", "pI", "strand")
 # threshold = 10 ^ (mean(log10(tab_lst[[i]][[5]])) + (3 * sd(log10(tab_lst[[i]][[5]]))))
#  print(paste0("outlier cutoff is: ", threshold))
  tab_lst[[i]] = tab_lst[[i]] |>
    filter(tab_lst[[i]][[5]] < 1000)
 #   filter(tab_lst[[i]][[5]] <= threshold)
  print(
    paste0(
      "The number of genes for ",
      names(tab_lst)[[i]],
      " is: ",
      dim(tab_lst[[i]])[1]
      )
    )
    print(summary(tab_lst[[i]][[5]]))
    tab_lst[[i]]$cell_line = names(tab_lst)[[i]]
    
  }
```

```{r}
pI_tab <- do.call(rbind, tab_lst)
```

Now I should be able to pivot that wider, though first of all filter

```{r}
pI_tab_wide <- pI_tab |> 
  pivot_wider(id_cols = c("chrom", "start", "end", "symbol", "strand"),
              names_from = cell_line,
              names_prefix = "pI_",
              values_from = pI,
              values_fill = NA
              )

```
This indicates 24050 total genes have been identified.
(How many are in more than one cell line? Not important at this point in the code
where we're treating these independently)

```{r rank order}
setDT(pI_tab_wide)
pI_tab_wide[, ':='(pI_ro_T47D=frank(pI_T47D, na.last="keep"), 
                             pI_ro_MB231=frank(pI_MB231, na.last="keep"),
                             pI_ro_SUM159=frank(pI_SUM159, na.last="keep"),
                             pI_ro_MCF7=frank(pI_MCF7, na.last="keep"),
                             pI_ro_MCF10A=frank(pI_MCF10A, na.last="keep"))]
```

```{r}
write.table(
  pI_tab,
  file = "peppro_pIs_w_rank.tsv",
  row.names = FALSE,
  sep = "\t",
  quote = FALSE
  )
```


```{r theme}
mytheme <- theme(
  panel.background=element_blank(),
  text=element_text(color="black",face="bold",family="sans"),
  axis.text=element_text(color="black"),
  axis.ticks=element_line(color="black"),
  plot.margin=unit(c(0.25, 0.25, .25, 0.25),"cm"),
  plot.title=element_text(vjust=2, hjust=0.5),
  panel.grid.major=element_blank(),
  panel.grid.minor=element_blank(),
  axis.title.y=element_text(vjust=0),
  axis.title.x=element_text(vjust=0),
  panel.border = element_blank(),
  axis.line=element_line()
)
```




```{r}
MB231_hs <- ggplot(data=pI_tab_wide) +
  geom_point(aes(y=(pI_MB231/max(pI_MB231, na.rm=TRUE)), x=pI_ro_MB231)) +
  mytheme + 
  xlab("pI_rank") +
  ylab("Fraction of max pI") +
  ggtitle("MB231")+
  geom_hline(aes(yintercept=0.1), linetype="dotted")
MB231_hs
```

```{r}
MCF10A_hs <- ggplot(data=pI_tab_wide) +
  geom_point(aes(y=(pI_MCF10A/max(pI_MCF10A, na.rm=TRUE)), x=pI_ro_MCF10A)) +
  mytheme + 
  xlab("pI_rank") +
  ylab("Fraction of max pI") +
  ggtitle("MCF10A")+
  geom_hline(aes(yintercept=0.1), linetype="dotted")
MCF10A_hs
```

```{r}
MCF7_hs <- ggplot(data=pI_tab_wide) +
  geom_point(aes(y=(pI_MCF7/max(pI_MCF7, na.rm=TRUE)), x=pI_ro_MCF7)) +
  mytheme + 
  xlab("pI_rank") +
  ylab("Fraction of max pI") +
  ggtitle("MCF7")+
  geom_hline(aes(yintercept=0.1), linetype="dotted")
MCF7_hs
```

```{r}
SUM159_hs <- ggplot(data=pI_tab_wide) +
  geom_point(aes(y=(pI_SUM159/max(pI_SUM159, na.rm=TRUE)), x=pI_ro_SUM159)) +
  mytheme + 
  xlab("pI_rank") +
  ylab("Fraction of max pI") +
  ggtitle("SUM159")+
  geom_hline(aes(yintercept=0.1), linetype="dotted")
SUM159_hs
```

```{r}
T47D_hs <- ggplot(data=pI_tab_wide) +
  geom_point(aes(y=(pI_T47D/max(pI_T47D, na.rm=TRUE)), x=pI_ro_T47D)) +
  mytheme + 
  xlab("pI_rank") +
  ylab("Fraction of max pI") +
  ggtitle("T47D")+
  geom_hline(aes(yintercept=0.1), linetype="dotted")
T47D_hs
```

```{r pdf_output}
pdf(file = "project_cell_lines_hockey_sticks.pdf", width = 7)
T47D_hs
MB231_hs
SUM159_hs
MCF7_hs
MCF10A_hs
dev.off()
```


GSEA???
```{r subsets}
top_90perc_SUM159 <- pI_tab_wide |>
  filter(pI_SUM159 >= 0.1 * (max(pI_SUM159, na.rm=TRUE)))
top_90perc_T47D <- pI_tab_wide |>
  filter(pI_T47D >=  0.1 * (max(pI_T47D, na.rm=TRUE)))
top_90perc_MB231 <- pI_tab_wide |>
  filter(pI_MB231 >=  0.1 * (max(pI_MB231, na.rm=TRUE)))
top_90perc_MCF7 <- pI_tab_wide |>
  filter(pI_MCF7 >=  0.1 * (max(pI_MCF7, na.rm=TRUE)))
top_90perc_MCF10A <- pI_tab_wide |>
  filter(pI_MCF10A >=  0.1 * (max(pI_MCF10A, na.rm=TRUE)))
dim(top_90perc_SUM159)
dim(top_90perc_T47D)
dim(top_90perc_MB231)
dim(top_90perc_MCF7)
dim(top_90perc_MCF10A)
```
```{r}
library(AnnotationDbi)
library(org.Hs.eg.db)
library(enrichR)
```

```{r databases}
options(enrichR.base.address <- "https://amp.pharm.mssm.edu/Enrichr/")
dbs <-listEnrichrDbs()
```

```{r}
dbs <- c("GO_Molecular_Function_2021", "GO_Biological_Process_2021", "KEGG_2021_Human")
MCF7_list <- top_90perc_MCF7[[4]]
MCF7_enriched <- enrichr(MCF7_list, dbs)
SUM159_list <- top_90perc_SUM159[[4]]
SUM159_enriched <- enrichr(SUM159_list, dbs)
T47D_list <- top_90perc_T47D[[4]]
T47D_enriched <- enrichr(T47D_list, dbs)
MB231_list <- top_90perc_MB231[[4]]
MB231_enriched <- enrichr(MB231_list, dbs)
MCF10A_list <- top_90perc_MCF10A[[4]]
MCF10A_enriched <- enrichr(MCF10A_list, dbs)
```
LoL = list of lists
```{r}
LoL <- list(MCF7_enriched, SUM159_enriched, T47D_enriched, MB231_enriched, MCF10A_enriched)
dbs <- as.list(dbs)
line_ids <- list("MCF7", "SUM159", "T47D", "MB231", "MCF10A")
for (i in seq_along(LoL)){
  tmp = Map(cbind, LoL[[i]], db_id=dbs)
  tmp2 = do.call(rbind, tmp)
  LoL[[i]] = tmp2
  }
LoL2 <- Map(cbind, LoL, line_id=line_ids)
enrichment_tab <- do.call(rbind, LoL2)
```

```{r}
enrichment_tab <- enrichment_tab |> 
  dplyr::select(-c(5,6))
write.table(enrichment_tab, file="ontology.txt", quote=FALSE, sep="\t", row.names = FALSE)
```

```{r}
ont <- enrichment_tab |> 
  separate(col=2, into=c("num_genes_match", "num_genes_set"),
           sep = "/", remove=TRUE, convert=TRUE)
```

```{r}
ont_GO_biol <- ont[ont$db_id == "GO_Biological_Process_2021",]
```

```{r}
ont_GO_biol <- ont_GO_biol |>  
    group_by(line_id) |> 
    slice_min(P.value, n=10) |> 
    ungroup()
```


```{r}
#to make the p value scales better:
ont_GO_biol_MCF7 <- ggplot(data = ont_GO_biol[ont_GO_biol$line_id == "MCF7",]) +
  geom_col(
    aes(y = reorder(Term, P.value, decreasing = TRUE),
        x = num_genes_match, fill = P.value)
    ) +
  mytheme + 
  xlab("Counts in set") +
  ylab("Gene set") +
  ggtitle("GO_biol MCF7") +
  scale_y_discrete(labels = function(x) stringr::str_trunc(x, 30))
ont_GO_biol_MCF10A <- ggplot(data=ont_GO_biol[ont_GO_biol$line_id=="MCF10A",]) +
  geom_col(aes(y=reorder(Term, P.value, decreasing=TRUE), x=num_genes_match, fill=P.value)) +
  mytheme + 
  xlab("Counts in set") +
  ylab("Gene set") +
  ggtitle("GO_biol MCF10A") +
  scale_y_discrete(labels = function(x) stringr::str_trunc(x, 30))
ont_GO_biol_MB231 <- ggplot(data=ont_GO_biol[ont_GO_biol$line_id=="MB231",]) +
  geom_col(aes(y=reorder(Term, P.value, decreasing=TRUE), x=num_genes_match, fill=P.value)) +
  mytheme + 
  xlab("Counts in set") +
  ylab("Gene set") +
  ggtitle("GO_biol MB231") +
  scale_y_discrete(labels = function(x) stringr::str_trunc(x, 30))
ont_GO_biol_SUM159 <- ggplot(data=ont_GO_biol[ont_GO_biol$line_id=="SUM159",]) +
  geom_col(aes(y=reorder(Term, P.value, decreasing=TRUE), x=num_genes_match, fill=P.value)) +
  mytheme + 
  xlab("Counts in set") +
  ylab("Gene set") +
  ggtitle("GO_biol SUM159") +
  scale_y_discrete(labels = function(x) stringr::str_trunc(x, 30))
ont_GO_biol_T47D <- ggplot(data=ont_GO_biol[ont_GO_biol$line_id=="T47D",]) +
  geom_col(aes(y=reorder(Term, P.value, decreasing=TRUE), x=num_genes_match, fill=P.value)) +
  mytheme + 
  xlab("Counts in set") +
  ylab("Gene set") +
  ggtitle("GO_biol T47D") +
  scale_y_discrete(labels = function(x) stringr::str_trunc(x, 30))
ont_GO_biol_MCF7
ont_GO_biol_MCF10A
ont_GO_biol_MB231
ont_GO_biol_SUM159
ont_GO_biol_T47D
```

```{r ontology_pdf}
pdf(file="project_cell_lines_ontology.pdf", width = 15)
ont_GO_biol_MCF7
ont_GO_biol_MCF10A
ont_GO_biol_MB231
ont_GO_biol_SUM159
ont_GO_biol_T47D
dev.off()
```

```{r}
circle_plot_MCF7 <- ggplot(data=ont_GO_biol[ont_GO_biol$line_id=="MCF7",]) +
  geom_point(aes(y=reorder(Term, Odds.Ratio),
                 x=Odds.Ratio, color=Adjusted.P.value,
                 size=(num_genes_match/num_genes_set*100))) +
  mytheme + 
  xlab("Odds Ratio") +
  ylab("Gene set") +
  ggtitle("GO_biol MCF7") +
  scale_y_discrete(labels = function(x) stringr::str_trunc(x, 30)) +
  scale_color_continuous(name="Adj.P.Value") + 
  scale_size_continuous(name="Geneset %")
circle_plot_MCF10A <- ggplot(data=ont_GO_biol[ont_GO_biol$line_id=="MCF10A",]) +
  geom_point(aes(y=reorder(Term, Odds.Ratio),
                 x=Odds.Ratio, color=Adjusted.P.value,
                 size=(num_genes_match/num_genes_set*100))) +
  mytheme + 
  xlab("Odds Ratio") +
  ylab("Gene set") +
  ggtitle("GO_biol MCF10A") +
  scale_y_discrete(labels = function(x) stringr::str_trunc(x, 30)) +
  scale_color_continuous(name="Adj.P.Value") + 
  scale_size_continuous(name="Geneset %")
circle_plot_MB231 <- ggplot(data=ont_GO_biol[ont_GO_biol$line_id=="MB231",]) +
  geom_point(aes(y=reorder(Term, Odds.Ratio),
                 x=Odds.Ratio, color=Adjusted.P.value,
                 size=(num_genes_match/num_genes_set*100))) +
  mytheme + 
  xlab("Odds Ratio") +
  ylab("Gene set") +
  ggtitle("GO_biol MB231") +
  scale_y_discrete(labels = function(x) stringr::str_trunc(x, 30)) +
  scale_color_continuous(name="Adj.P.Value") + 
  scale_size_continuous(name="Geneset %")
circle_plot_SUM159 <- ggplot(data=ont_GO_biol[ont_GO_biol$line_id=="SUM159",]) +
  geom_point(aes(y=reorder(Term, Odds.Ratio),
                 x=Odds.Ratio, color=Adjusted.P.value,
                 size=(num_genes_match/num_genes_set*100))) +
  mytheme + 
  xlab("Odds Ratio") +
  ylab("Gene set") +
  ggtitle("GO_biol SUM159") +
  scale_y_discrete(labels = function(x) stringr::str_trunc(x, 30)) +
  scale_color_continuous(name="Adj.P.Value") + 
  scale_size_continuous(name="Geneset %")
circle_plot_T47D <- ggplot(data=ont_GO_biol[ont_GO_biol$line_id=="T47D",]) +
  geom_point(aes(y=reorder(Term, Odds.Ratio),
                 x=Odds.Ratio, color=Adjusted.P.value,
                 size=(num_genes_match/num_genes_set*100))) +
  mytheme + 
  xlab("Odds Ratio") +
  ylab("Gene set") +
  ggtitle("GO_biol T47D") +
  scale_y_discrete(labels = function(x) stringr::str_trunc(x, 30)) +
  scale_color_continuous(name="Adj.P.Value") + 
  scale_size_continuous(name="Geneset %")
circle_plot_MCF7
circle_plot_MCF10A
circle_plot_MB231
circle_plot_SUM159
circle_plot_T47D
```

```{r circle_ontology_pdf}
pdf(file = "project_cell_lines_circleplot_ontology.pdf", width = 15)
circle_plot_MCF7
circle_plot_MCF10A
circle_plot_MB231
circle_plot_SUM159
circle_plot_T47D
dev.off()
```
Alright, let's grab rankdif.


```{r}
pI_tab_wide$rankdif_MCF7vsSUM <- pI_tab_wide$pI_ro_MCF7 - pI_tab_wide$pI_ro_SUM159
pI_tab_wide$rankdif_T47DvsMB231 <- pI_tab_wide$pI_ro_T47D - pI_tab_wide$pI_ro_MB231
```

```{r}
pI_tab_wide$absrankdif_MCF7vsSUM <- abs(pI_tab_wide$rankdif_MCF7vsSUM)
pI_tab_wide$absrankdif_T47DvsMB231 <- abs(pI_tab_wide$rankdif_T47DvsMB231)
```

```{r}
write.table(pI_tab_wide, file="project_cell_lines_pI_withrankdif.txt", quote=FALSE, sep="\t", row.names = FALSE)
```

Now for clustering

```{r take out X and Y}
pI_tab_simple <- pI_tab_wide |> 
  filter(!grepl('chrY|chrX', chrom))
```

```{r}
pI_tab_simple_log10 <- cbind(
  pI_tab_simple[,1:5], log10(as.matrix(pI_tab_simple[,6:10]))
  )
```
Don't need ranks or anything for this one.
```{r}
pI_simple_log10 <- pI_tab_simple_log10 |> 
  rowwise() |> 
  mutate(stdev = sd(c(pI_MCF7, pI_SUM159, pI_MCF10A, pI_T47D, pI_MB231),
                    na.rm=TRUE),
         meanpi = mean(c(pI_MCF7, pI_SUM159, pI_MCF10A, pI_T47D, pI_MB231),
                       na.rm = TRUE),
         pivar = var(c(pI_MCF7, pI_SUM159, pI_MCF10A, pI_T47D, pI_MB231),
                     na.rm = TRUE)) |> 
  ungroup()
```
(Need ungroup, otherwise is rowwise df and causes problems later)
Remove genes with NA:

```{r c5}
pI_no_na <- pI_simple_log10 |>  
            filter(!is.na(pI_MCF7) &
                     !is.na(pI_SUM159) &
                     !is.na(pI_MCF10A) &
                     !is.na(pI_T47D) &
                     !is.na(pI_MB231)                   )
```

Only 1276 genes??? Did not expect that honestly...Let's just cluster with all of them then???
Can always venn diagram too?

```{r}
pI_norm <- pI_no_na |> 
  rowwise() |> 
  mutate(MB231norm = (pI_MB231 - meanpi) / stdev,
        MCF10Anorm = (pI_MCF10A - meanpi) / stdev,
        MCF7norm = (pI_MCF7 - meanpi) / stdev,
         SUM159norm = (pI_SUM159 - meanpi) / stdev,
         T47Dnorm = (pI_T47D - meanpi) / stdev) |> 
  ungroup()
```

Normalized matrix:
```{r}
simple_mat <- as.matrix(pI_norm[,14:18])
rownames(simple_mat) <- pI_norm[[4]]
colnames(simple_mat) <- c("MB231", "MCF10A", "MCF7", "SUM159", "T47D")
```

Not normalized matrix:
```{r}
simple_mat_nn <- as.matrix(pI_norm[,6:10])
rownames(simple_mat) <- pI_norm[[4]]
colnames(simple_mat) <- c("MB231", "MCF10A", "MCF7", "SUM159", "T47D")
```


```{r}
heatmap(simple_mat, scale="none", cexCol = 0.8, labRow = "", main = "row-normalized (calculated)", na.rm = TRUE)
```
```{r}
heatmap(simple_mat_nn, scale="none", cexCol = 0.8, labRow = "", main = "not normalized", na.rm = TRUE)
```
```{r}
heatmap(simple_mat_nn, scale="row", cexCol = 0.8, labRow = "", main = "row-normalized (function)", na.rm = TRUE)
```

The third one is technically the one Paula wanted, so:
```{r}
hm <- heatmap(simple_mat_nn, scale="row", cexCol = 0.8, labRow = "", main = "pI clustering (n=1276)", na.rm = TRUE)
pdf(file = "cluster.pdf", width = 15)
hm
dev.off()
```

Over 24K genes, only 1.2K share a pause. Why???
Venn diagram time...Probably easiest with a set of true_false bool columns

```{r}
pI_tab_simple$MB231_tf <- !is.na(pI_tab_simple$pI_MB231)
```

Works great, do for rest.
```{r}
pI_tab_simple$MCF10A_tf <- !is.na(pI_tab_simple$pI_MCF10A)
pI_tab_simple$MCF7_tf <- !is.na(pI_tab_simple$pI_MCF7)
pI_tab_simple$SUM159_tf <- !is.na(pI_tab_simple$pI_SUM159)
pI_tab_simple$T47D_tf <- !is.na(pI_tab_simple$pI_T47D)
```

```{r}
install.packages("venn")
```

```{r}
library(venn)
```

```{r}
tf_mat <- pI_tab_simple[,20:24]
colnames(tf_mat) <- c("MB231", "MCF10A", "MCF7", "SUM159", "T47D")
```

```{r}
venn(tf_mat)
```
Nice! Refine it...

```{r}
pI_venn = venn(tf_mat, zcolor = "style", box = FALSE)
```
```{r}
pdf(file = "venn.pdf", width = 15)
pI_venn
dev.off()
```

