---
title: "Peppro noncoding portion?"
output: html_notebook
---

```{r}
library(tidyverse)
library(biomaRt)
```

```{r}
peppro_pIs_w_rank <- read.delim("C:/Users/kayle/Box/Vertinolab/GenomicSandbox/project_cell_lines/ProSeq/Peppro_analysis/peppro_pIs_w_rank.tsv")
```

```{r}
peppro_wide <- peppro_pIs_w_rank |> 
  pivot_wider(id_cols = c("chrom", "symbol", "strand"),
              names_from = cell_line,
              names_prefix = "pI_",
              values_from = pI,
              values_fill = NA
              )
```

code help: https://support.bioconductor.org/p/124462/
```{r}
mart <- useMart("ENSEMBL_MART_ENSEMBL", host = "https://useast.ensembl.org")
```

```{r}
mart <- useDataset("hsapiens_gene_ensembl", mart)
```

```{r}
annotLookup <- getBM(
  mart = mart,
  attributes = c(
    "hgnc_symbol",
    "gene_biotype"),
  filter = "hgnc_symbol",
  values = peppro_wide$symbol,
  uniqueRows=TRUE)
```

```{r}
peppro_anno <- merge(peppro_wide, annotLookup, by.x = "symbol",
                     by.y = "hgnc_symbol", all = TRUE)
```

```{r}
protein_coding <- peppro_anno |> 
  filter(gene_biotype == "protein_coding")
print("protein coding:")
dim(protein_coding)
```

```{r}
non_coding <- peppro_anno |> 
  filter(gene_biotype != "protein_coding" & !is.na(gene_biotype))
print("noncoding:")
dim(non_coding)
```

```{r}
no_anno <- peppro_anno |> 
  filter(is.na(gene_biotype))
print("no anno")
dim(no_anno)
```
So what are these things I could not find an annotation for? ACsomelongnumber represents a solid 1800 of it, then there's many more hundreds of ALsomelongnumber and the like - at a glance, only things that jump out at me as *potential* real genes are AKAP2, AARS, APOPT1, ASNA1, DARS, a handful of CCDC and FAM and HIST proteins...A few others, but I'm not going to type all of them. I'd venture a guess that only maybe 50 genes there don't have orf, linc, or two letters then a long number in their signal, and I'm okay with throwing away that small handful for now.

```{r rank order}
setDT(protein_coding)
protein_coding[, ':='(pI_ro_T47D=frank(pI_T47D, na.last="keep"), 
                             pI_ro_MB231=frank(pI_MB231, na.last="keep"),
                             pI_ro_SUM159=frank(pI_SUM159, na.last="keep"),
                             pI_ro_MCF7=frank(pI_MCF7, na.last="keep"),
                             pI_ro_MCF10A=frank(pI_MCF10A, na.last="keep"))]
```


```{r}
protein_coding$rankdif_MCF7vsSUM <- protein_coding$pI_ro_MCF7 - protein_coding$pI_ro_SUM159
protein_coding$rankdif_T47DvsMB231 <- protein_coding$pI_ro_T47D - protein_coding$pI_ro_MB231
```

```{r}
protein_coding$absrankdif_MCF7vsSUM <- abs(protein_coding$rankdif_MCF7vsSUM)
protein_coding$absrankdif_T47DvsMB231 <- abs(protein_coding$rankdif_T47DvsMB231)
```

```{r}
write.table(protein_coding, file="protein_coding_peppro_withrankdif.txt", quote=FALSE, sep="\t", row.names = FALSE)
```

Now for clustering

```{r take out X and Y}
pI_tab_simple <- protein_coding |> 
  filter(!grepl('chrY|chrX', chrom))
```

```{r}
pI_tab_simple_log10 <- cbind(
  pI_tab_simple[,1:3], log10(as.matrix(pI_tab_simple[,4:8]))
  )
```

```{r}
pI_simple_log10 <- pI_tab_simple_log10 |> 
  rowwise() |> 
  mutate(stdev = sd(c(pI_MCF7, pI_SUM159, pI_MCF10A, pI_T47D, pI_MB231),
                    na.rm=TRUE),
         meanpi = mean(c(pI_MCF7, pI_SUM159, pI_MCF10A, pI_T47D, pI_MB231),
                       na.rm = TRUE),
         pivar = var(c(pI_MCF7, pI_SUM159, pI_MCF10A, pI_T47D, pI_MB231),
                     na.rm = TRUE)) |> 
  ungroup()
```
(Need ungroup, otherwise is rowwise df and causes problems later)
Remove genes with NA:

```{r c5}
pI_no_na <- pI_simple_log10 |>  
            filter(!is.na(pI_MCF7) &
                     !is.na(pI_SUM159) &
                     !is.na(pI_MCF10A) &
                     !is.na(pI_T47D) &
                     !is.na(pI_MB231)                   )
```

4685 genes, not the 1k something I had previously
Can always venn diagram too?

```{r}
pI_norm <- pI_no_na |> 
  rowwise() |> 
  mutate(MB231norm = (pI_MB231 - meanpi) / stdev,
        MCF10Anorm = (pI_MCF10A - meanpi) / stdev,
        MCF7norm = (pI_MCF7 - meanpi) / stdev,
         SUM159norm = (pI_SUM159 - meanpi) / stdev,
         T47Dnorm = (pI_T47D - meanpi) / stdev) |> 
  ungroup()
```

Normalized matrix:
```{r}
simple_mat <- as.matrix(pI_norm[,12:16])
rownames(simple_mat) <- pI_norm[[4]]
colnames(simple_mat) <- c("MB231", "MCF10A", "MCF7", "SUM159", "T47D")
```

Not normalized matrix:
```{r}
simple_mat_nn <- as.matrix(pI_norm[,4:8])
rownames(simple_mat) <- pI_norm[[4]]
colnames(simple_mat) <- c("MB231", "MCF10A", "MCF7", "SUM159", "T47D")
```


```{r}
heatmap(simple_mat, scale="none", cexCol = 0.8, labRow = "", main = "row-normalized (calculated)", na.rm = TRUE)
```

```{r}
heatmap(simple_mat_nn, scale="row", cexCol = 0.8, labRow = "", main = "row-normalized (calculated)", na.rm = TRUE)
```


```{r}
pI_tab_simple$MB231_tf <- !is.na(pI_tab_simple$pI_MB231)
pI_tab_simple$MCF10A_tf <- !is.na(pI_tab_simple$pI_MCF10A)
pI_tab_simple$MCF7_tf <- !is.na(pI_tab_simple$pI_MCF7)
pI_tab_simple$SUM159_tf <- !is.na(pI_tab_simple$pI_SUM159)
pI_tab_simple$T47D_tf <- !is.na(pI_tab_simple$pI_T47D)
```


```{r}
library(venn)
```

```{r}
tf_mat <- pI_tab_simple[,19:23]
colnames(tf_mat) <- c("MB231", "MCF10A", "MCF7", "SUM159", "T47D")
```


```{r}
pI_venn_peppro = venn(tf_mat, zcolor = "style", box = FALSE)
```

```{r}
pdf(file = "venn_peppro.pdf", width = 15)
pI_venn_peppro
dev.off()
```

```{r}
simple_top500 <- pI_no_na |> 
  arrange(desc(pivar)) |>  
  dplyr::slice(c(1:500))
```

```{r}
pI_norm <- simple_top500 |> 
  rowwise() |> 
  mutate(MB231norm = (pI_MB231 - meanpi) / stdev,
        MCF10Anorm = (pI_MCF10A - meanpi) / stdev,
        MCF7norm = (pI_MCF7 - meanpi) / stdev,
         SUM159norm = (pI_SUM159 - meanpi) / stdev,
         T47Dnorm = (pI_T47D - meanpi) / stdev) |> 
  ungroup()
```

Normalized matrix:
```{r}
simple_mat <- as.matrix(pI_norm[,12:16])
rownames(simple_mat) <- pI_norm[[2]]
colnames(simple_mat) <- c("MB231", "MCF10A", "MCF7", "SUM159", "T47D")
```

```{r}
heatmap(simple_mat, scale="none", cexCol = 0.8, labRow = "", main = "row-normalized (calculated)", na.rm = TRUE)
```

Not normalized matrix:
```{r}
simple_mat <- as.matrix(pI_norm[,4:8])
rownames(simple_mat) <- pI_norm[[2]]
colnames(simple_mat) <- c("MB231", "MCF10A", "MCF7", "SUM159", "T47D")
```

```{r}
heatmap(simple_mat, scale="row", cexCol = 0.8, labRow = "", main = "row-norm (function)", na.rm = TRUE)
```