---
title: "Analysis of Cell lines w/ and w/out H4K20me3"
output: html_notebook
---

```{r}
library(tidyverse)
library(data.table)
```

```{r}
DIR <- "C:/Users/kayle/Box/Vertinolab/GenomicSandbox/project_cell_lines/ProSeq/PEPPRO_SE/"
MB231_pI <- read.delim(
  paste0(DIR, "MB231/QC_hg38/MB231_pause_index.bed.gz"),
  header = FALSE,
  skipNul = TRUE
  )
MCF7_pI <- read.delim(
  paste0(DIR, "MCF7/QC_hg38/MCF7_pause_index.bed.gz"),
  header = FALSE,
  skipNul = TRUE
  )
SUM159_pI <- read.delim(
  paste0(DIR, "SUM159/QC_hg38/SUM159_pause_index.bed.gz"),
  header = FALSE,
  skipNul = TRUE
  )
T47D_pI <- read.delim(
  paste0(DIR, "T47D/QC_hg38/T47D_pause_index.bed.gz"),
  header = FALSE,
  skipNul = TRUE
  )
```

```{r}
tab_lst <- list(MB231 = MB231_pI,
               MCF7 = MCF7_pI,
               SUM159 = SUM159_pI,
               T47D = T47D_pI)
for (i in seq_along(tab_lst)) {
  colnames(tab_lst[[i]]) = c("chrom", "start", "end", "symbol", "pI", "strand")
  tab_lst[[i]] = tab_lst[[i]] |>
    filter(tab_lst[[i]][[5]] < 1000)
  plus = tab_lst[[i]] |>
    filter(tab_lst[[i]][[6]] == "+")
  plus$end = plus$start + 2000
  plus$start = plus$start - 2000
  minus = tab_lst[[i]] |>
    filter(tab_lst[[i]][[6]] == "-")
  minus$start = minus$end - 2000
  minus$end = minus$end + 2000
  tab_lst[[i]] = rbind(plus, minus)
}
MB231 <- tab_lst[[1]]
MCF7 <- tab_lst[[2]]
SUM159 <- tab_lst[[3]] 
T47D <- tab_lst[[4]] 
```


```{r}
write.table(
  MB231,
  file = "MB231_promoters.tsv",
  row.names = FALSE,
  col.names = FALSE,
  sep = "\t",
  quote = FALSE
  )
write.table(
  MCF7,
  file = "MCF7_promoters.tsv",
  row.names = FALSE,
  col.names = FALSE,
  sep = "\t",
  quote = FALSE
  )
write.table(
  SUM159,
  file = "SUM159_promoters.tsv",
  row.names = FALSE,
  col.names = FALSE,
  sep = "\t",
  quote = FALSE
  )
write.table(
  T47D,
  file = "T47D_promoters.tsv",
  row.names = FALSE,
  col.names = FALSE,
  sep = "\t",
  quote = FALSE
  )
```

Okay, now I take these files into bluehive to run bedtools intersect on them.
Did bedtools intersect -a promoters -b peaks -c, which means keep all promoters, report number of hits in peaks. Now bring them back in...

```{r merged}
DIR <- "C:/Users/kayle/Box/Vertinolab/McKayla Ford/Projects/Project_Cell_Lines/H4K20me3_status_pI/Merged_AB/Intersected_tabs/"
MB231_merge <- read.delim(
  paste0(DIR, "MB231_pI_MB231s.tsv"),
  header = FALSE
  )
MCF7_merge <- read.delim(
  paste0(DIR, "MCF7_pI_MCF7s.tsv"),
  header = FALSE
  )
SUM159_merge <- read.delim(
  paste0(DIR, "SUM159_pI_SUM159s.tsv"),
  header = FALSE
  )
T47D_merge <- read.delim(
  paste0(DIR, "T47D_pI_T47Ds.tsv"),
  header = FALSE
  )
```

```{r abcam}
DIR <- "C:/Users/kayle/Box/Vertinolab/McKayla Ford/Projects/Project_Cell_Lines/H4K20me3_status_pI/Abcam/Intersected_peaks/"
MB231_abcam <- read.delim(
  paste0(DIR, "MB231_abcam_pI.tsv"),
  header = FALSE
  )
MCF7_abcam <- read.delim(
  paste0(DIR, "MCF7_abcam_pI.tsv"),
  header = FALSE
  )
SUM159_abcam <- read.delim(
  paste0(DIR, "SUM159_abcam_pI.tsv"),
  header = FALSE
  )
T47D_abcam <- read.delim(
  paste0(DIR, "T47D_abcam_pI.tsv"),
  header = FALSE
  )
```

```{r cellsignaling}
DIR <- "C:/Users/kayle/Box/Vertinolab/McKayla Ford/Projects/Project_Cell_Lines/H4K20me3_status_pI/Cell_signalling/Intersected_peaks/"
MB231_cell <- read.delim(
  paste0(DIR, "MB231_cellsignaling_pI.tsv"),
  header = FALSE
  )
MCF7_cell <- read.delim(
  paste0(DIR, "MCF7_cellsignaling_pI.tsv"),
  header = FALSE
  )
SUM159_cell <- read.delim(
  paste0(DIR, "SUM159_cellsignaling_pI.tsv"),
  header = FALSE
  )
T47D_cell <- read.delim(
  paste0(DIR, "T47D_cellsignaling_pI.tsv"),
  header = FALSE
  )
```

```{r}
library(biomaRt)
mart <- useMart("ENSEMBL_MART_ENSEMBL", host = "https://useast.ensembl.org")
mart <- useDataset("hsapiens_gene_ensembl", mart)
```


```{r}
H4K20me3POS_lst <- list(MB231_merge = MB231_merge,
               MCF7_merge = MCF7_merge,
               SUM159_merge = SUM159_merge,
               T47D_merge = T47D_merge,
               MB231_abcam = MB231_abcam,
               MCF7_abcam = MCF7_abcam,
               SUM159_abcam = SUM159_abcam,
               T47D_abcam = T47D_abcam,
               MB231_cell = MB231_cell,
               MCF7_cell = MCF7_cell,
               SUM159_cell = SUM159_cell,
               T47D_cell = T47D_cell)
H4K20me3NEG_lst <- H4K20me3POS_lst
for (i in seq_along(H4K20me3POS_lst)) {
  colnames(H4K20me3POS_lst[[i]]) = c("chrom", "start", "end", "symbol", "pI", "strand", "score")
    annotLookup = getBM(
    mart = mart,
    attributes = c(
      "hgnc_symbol",
      "gene_biotype"),
    filter = "hgnc_symbol",
    values = H4K20me3POS_lst[[i]]$symbol,
    uniqueRows=TRUE)
  H4K20me3POS_lst[[i]] <- merge(H4K20me3POS_lst[[i]], annotLookup, by.x = "symbol",
                     by.y = "hgnc_symbol", all = TRUE)
 H4K20me3POS_lst[[i]] = H4K20me3POS_lst[[i]] |>
    filter(H4K20me3POS_lst[[i]][[7]] > 0 & H4K20me3POS_lst[[i]][[8]] == "protein_coding")
   print(
    paste0(
      "Length of POS ",
      names(H4K20me3POS_lst)[[i]],
      " is: ",
      dim(H4K20me3POS_lst[[i]])[1]
      )
    )
  colnames(H4K20me3NEG_lst[[i]]) = c("chrom", "start", "end", "symbol", "pI", "strand", "score")
  H4K20me3NEG_lst[[i]] <- merge(H4K20me3NEG_lst[[i]], annotLookup, by.x = "symbol",
                     by.y = "hgnc_symbol", all = TRUE)
  H4K20me3NEG_lst[[i]] = H4K20me3NEG_lst[[i]] |>
    filter(H4K20me3NEG_lst[[i]][[7]] == 0 & H4K20me3NEG_lst[[i]][[8]] == "protein_coding")
  print(
    paste0(
      "Length of NEG ",
      names(H4K20me3NEG_lst)[[i]],
      " is: ",
      dim(H4K20me3NEG_lst[[i]])[1]
      )
    )
}
```

So in general, most genes don't have an intersecting H4K20me3 peak in cell signalling, but many do in abcam. What portion is protein coding?


```{r}
mytheme = theme(
  panel.background=element_blank(),
  text=element_text(color="black",face="bold",family="sans"),
  axis.text=element_text(color="black"),
  axis.ticks=element_line(color="black"),
  plot.margin=unit(c(0.25, 0.25, .25, 0.25),"cm"),
  plot.title=element_text(vjust=2, hjust=0.5),
  panel.grid.major=element_blank(),
  panel.grid.minor=element_blank(),
  axis.title.y=element_text(vjust=0),
  axis.title.x=element_text(vjust=0),
  panel.border = element_blank(),
  axis.line=element_line()
)
colors <- c("H4K20me3 Positive" = "blue", "H4K20me3 Negative" = "red")
```

```{r}
H4K20me3pval_lst <- list(1:12)
for (i in seq_along(H4K20me3POS_lst)) {
  test = wilcox.test(x = H4K20me3POS_lst[[i]]$pI, y = H4K20me3NEG_lst[[i]]$pI, paired = FALSE,
            conf.int = TRUE, correct = FALSE)
  H4K20me3pval_lst[[i]] = test$p.value
}
```

So anyway, add p value to the plots? Need to look into further for proper display (probably will need to change these graphs for publishing anyway) so for now we'll just do element.text
```{r}
title_list <- list("MB231 (Merged Antibodies)",
                   "MCF7 (Merged Antibodies)", 
                   "SUM159 (Merged Antibodies)",
                   "T47D (Merged Antibodies)",
                   "MB231 (Abcam)", 
                   "MCF7 (Abcam)",
                   "SUM159 (Abcam)",
                   "T47D (Abcam)",
                   "MB231 (Cell Signalling)",
                   "MCF7 (Cell Signalling)",
                   "SUM159 (Cell Signalling)",
                   "T47D (Cell Signalling)")
gplot = title_list

for (i in seq_along(H4K20me3POS_lst)) {
  message(i)
  gplot[[i]] <- local({
    i <- i
    gplot <- ggplot() +
  stat_ecdf(geom="step", data = H4K20me3POS_lst[[i]], aes(pI, color = "H4K20me3 Positive")) +
  stat_ecdf(geom="step", data = H4K20me3NEG_lst[[i]], aes(pI, color = "H4K20me3 Negative")) +
  mytheme +
  scale_x_log10(n.breaks=6, labels=scales::label_comma()) +
  ylab("Cumulative Distribution") +
  ggtitle(title_list[[i]]) +
  scale_color_manual(values = colors) +
  theme(legend.position = c(0.2, 0.8),
        legend.key = element_blank(),
        legend.title = element_blank()) +
  annotate("text", x = 0.8, y = 0.2, label = paste0("p=", signif(H4K20me3pval_lst[[i]], digits = 4)))
    print(gplot)
  })
}
```

```{r}
pdf(file = "cdf.pdf", width = 7)
for (i in seq_along(gplot)) {print(gplot[[i]])}
dev.off()
```
   
   