---
title: "Pausing index Project Cell Lines 2/13/2023"
output: html_notebook
---
#Note on R notebook for anyone else looking at it
Good way to keep my code documented with the products it produces. Used for
interactive scripts - stick to simple R scripts for source files. Unlike a normal
R markdown file, does not rerun all chunks when making the finished product. Instead, 
run the chunks like in a normal R script, then hit preview and it will take the material
you've already ran for the printout.

```{r sourcecode}
source("~/Script repository/R scripting/My_Useful_Fns.R") #12/09/2022 commit at my github https://github.com/McK-Ford/Script-repository/blob/main/R%20scripting/My_Useful_Fns.R
enableJIT(3)
```

```{r}
cell_lines_pI_3_no_filter <- read.delim("C:/Users/kayle/Box/Vertinolab/GenomicSandbox/project_cell_lines/ProSeq/pI/V3/cell_lines_pI_3_no_filter.txt")
peppro_pIs_w_rank <- read.delim("C:/Users/kayle/Box/Vertinolab/GenomicSandbox/project_cell_lines/ProSeq/Peppro_analysis/peppro_pIs_w_rank.tsv")
```

No filter is 19597. Peppro pIs needs to be pivoted before I can count it.

```{r}
cell_lines_pI_3_no_filter <- cell_lines_pI_3_no_filter |> 
  select(-c(13:14, 16:17,
            19:20, 22:23,
            25:26, 28:29,
            31:32, 34:35,
            37:38, 40:41)) |> 
  separate(col=symbol, into=c("symbol", "TSS"),
           sep = "_", remove=TRUE) |> 
  select(-c(5:6))
```
```{r}
peppro <- peppro_pIs_w_rank |> 
  pivot_wider(names_from = cell_line, names_prefix = "pI", names_sep = ".",
              values_from = pI, values_fill = NA)
```

peppro is 24050 but I think that includes unique TSSes... oooh is that a problem with my initial analysis...Now that I think of it...oh for Fs sake could that be why those are so different...
```{r}
peppro <- peppro_pIs_w_rank |> 
  select(-c(2:3)) |> 
    pivot_wider(names_from = cell_line, names_prefix = "pI", names_sep = ".",
              values_from = pI, values_fill = NA)
```
Yeah once we stop caring about dif TSS for same gene it's 13K.

```{r}
mergetab = merge(cell_lines_pI_3_no_filter, peppro, by = "symbol", all = TRUE, suffixes = c("_V3", "_peppro"))
```

```{r}
V3_only = mergetab |>
  filter(is.na(chrom_peppro))
peppro_only = mergetab |>
  filter(is.na(chrom_V3))
in_both = mergetab |>
  filter(!is.na(chrom_V3) & !is.na(chrom_peppro))
```

```{r}
print("V3_only")
dim(V3_only)
print("MCF7")
summary(V3_only$MCF7.pI)
print("MB231")
summary(V3_only$MB231.pI)

print("peppro_only")
dim(peppro_only)
print("MCF7")
summary(peppro_only$pIMCF7)
print("MB231")
summary(peppro_only$pIMB231)

print("in_both")
dim(in_both)
print("MCF7, V3")
summary(in_both$MCF7.pI)
print("MCF7, peppro")
summary(in_both$pIMCF7)
print("MB231, V3")
summary(in_both$MB231.pI)
print("MB231, peppro")
summary(in_both$pIMB231)
```
how much of v3 only would have been filtered out anyway by my stuff? Filters were all are NA, no Inf, total norm above 1, remove everything is 0. (Okay, don't normally do this for calculation purposes, but we can do 0 as NA to filter out the 'everything is 0' scenarios just to get numbers)

```{r}
v3_only_long = V3_only |> 
  select(-c(22:28)) |>
  pivot_longer(cols=c(12:21), names_to = c("cell_line", ".value"), names_pattern = "(.+)\\.(.+)") |>
  filter(!is.na(pI) & pI!="Inf" & total_norm>=1) |> 
  select(-c(total_norm))
```

```{r output}
V3_only2 = v3_only_long |>
  pivot_wider(values_from = pI, names_from = cell_line, values_fill = NA) |>
  rowwise() |>
  filter(sum(MCF7, MCF10A, MB231, T47D, SUM159, na.rm = TRUE) > 0) |>
  ungroup()
dim(V3_only2)
```
678 genes that are only found in V3 not Peppro post our agreed filtering measures, instead of the previous 9K. So most of the missing genes just were filtered out by peppro like they were filtered by me.

Stuff that's only in peppro is harder to deal with because peppro doesn't give the same information V3 gives me back. I don't necessarily want to coding/noncoding annotate it right now, but at a glance, a lot of the symbols seen in it that are not seen in V3 look like non-coding RNA symbols (two letters then a string of numbers, somegene-ASI1, someothergeneLINC). Could try biomart?

```{r}
library(biomaRt)

```


As for stuff that's in both...no real need to do anything special with it... maybe comparative pIs later