---
title: "Sesame methylation mapping"
output: html_notebook
---

```{r}
library("sesame")
```
https://www.bioconductor.org/packages/release/bioc/vignettes/sesame/inst/doc/sesame.html
Okay. let's try their built in pipeline setup, then revise if it seems I need to tweak something they won't let me do in the overarching function.

```{r}
idat_dir <-  system.file("C:/Users/kayle/Box/Vertinolab/1Emory_Vertinolab/Illumina_Infinium_Methylation_Analyses/MCF7 MB231 DAC DOT1L EPIC ARRAYS PVE11277/", package = "sesameData")
```

func options get beta values or get AFs, if nul then return SigDF list (the tool for further analysis)
```{r}
betas <- openSesame(idat_dir, BPPARAM = BiocParallel::MulticoreParam(2))
```
Okay, I see their breakdown in the manual, but what exactly is the problem?
With readIDATpair, "the function takes a prefix string that is shared with _Grn.idat and _Red.idat, then returns a SigDF. I see. I have _grn and _red with matching strings but maybe it's confused because there's multiple in one directory?

Does it function better if we break the function down into its constituent parts? There's options if I do that for a design manifest too which may help.
```{r}
betas <- do.call(
  cbind,
  BiocParallel::bplapply(
    searchIDATprefixes(idat_dir),
    function(pfx) {
      getBetas(prepSesame(
        readIDATpair(pfx), prep = "QCDPB"
        )
        )
        },
    BPPARM = BiocParallel::MulticoreParam(2)
    )
  )
```
Dir does not exist? It's not a typo...

Wait, I'm an idiot. I think I somehow got confused by their package data loading tool when what I should have done is:
```{r}
idat_dir <- "C:/Users/kayle/Box/Vertinolab/1Emory_Vertinolab/Illumina_Infinium_Methylation_Analyses/MCF7 MB231 DAC DOT1L EPIC ARRAYS PVE11277/"
```
then
```{r}
betas <- openSesame(idat_dir, BPPARAM = BiocParallel::MulticoreParam(2))
```

Okay, parallel can't work the way they want in windows, go back and implement properly later, for now just go single threaded and see if the cache is still a problem because I did try caching the data already.
```{r}
betas <- openSesame(idat_dir)
```

```{r}
library(ExperimentHub)
sesameDataCache()
```
FFS.
Okay, I think I found some relevant info. Just check first:
```{r}
packageVersion("ExperimentHub")
packageVersion("BiocFileCache")
packageVersion("dbplyr")
```
Yeah, I see.
https://stackoverflow.com/questions/77370659/error-failed-to-collect-lazy-table-caused-by-error-in-db-collect-using
https://github.com/Bioconductor/BiocFileCache/pull/50
https://github.com/zwdzwd/sesame/issues/120

So dbplyr updated, broke a lot of things (including biomart and stuff too- this is worth forwarding to the others, I think.)
