---
title: "G4 signal analysis"
output: html_notebook
---

```{r loading, message=FALSE, warning=FALSE}
library( tidyverse )
```

```{r source, message=FALSE, warning=FALSE}
source( "~/Script repository/R scripting/Matrix_Fns.R" ) #5/2/23 commit at my github https://github.com/McK-Ford/Script-repository/blob/main/R%20scripting/Matrix.R
source( "~/Script repository/R scripting/Graphing_Functions.R" )
```


```{r}
mygenes <- fread( 
  file = "C:/Users/kayle/Box/Vertinolab/McKayla Ford/Projects/R-loops_Pausing/Sequence_based_analysis/Classing_by_Skew/beds/skew_classed_refseq_wheader.txt"
  )
```

Bed filtering 1
```{r}
gene_info_p <- mygenes |> filter( strand == "+" & chrom != "chrX" & gene_l > 150 )
gene_info_m <- mygenes |> filter( strand == "-" & chrom != "chrX" & gene_l > 150 )
```


If I do G4 eCDF prox/dist ratio:
For TSS regions (to get pause index, tss regions divided by gene body regions...)
this isnt' actually prox dist, names are wrong
```{r}
TSS_p <- gene_info_p |>
  select( c( "chrom", "gene_s", "cpg_e", "uniq_id", "TSS_skew", "strand" ) )
TSS_m <- gene_info_m |>
  select( c( "chrom",  "cpg_s", "gene_e", "uniq_id", "TSS_skew", "strand" ) )

colnames( TSS_p ) <- c(
    "chrom",
    "start",
    "end",
    "uniq_id",
    "score",
    "strand"
    )
colnames( TSS_m ) <- c(
    "chrom",
    "start",
    "end",
    "uniq_id",
    "score",
    "strand"
    )
```

```{r}
TSS_p$end <- TSS_p$start + 100
TSS_m$start <- TSS_m$end - 100
```

```{r}
DIR <- "C:/Users/kayle/Box/Vertinolab/McKayla Ford/Data/CutnTag_n_chip/PublicData/GSE178688_Lyu_2021_HEK293T_G4_CnTandChIPseq/"
```


```{r}
TSS_tab <- rbind(TSS_p, TSS_m)

CnT_TSS_tab <- score_matrix(
      bed = TSS_tab,
      readsource = paste0( DIR, "GSM5395699_CUT-Tag-BG4.bw" ),
      n = 1,
      ignorestrand = TRUE,
      method = "bi_anch",
      bam_or_bw = "bw"
      )
```

```{r}
colnames(CnT_TSS_tab) = c(colnames(CnT_TSS_tab[,1:6]), "TSSscore")
```

for legibility...
```{r}
CnT_TSS_tab$TSSscore <- CnT_TSS_tab$TSSscore * 1000
```

For 3' CGI
```{r}
cgi3_p <- gene_info_p |>
  select( c( "chrom", "gene_s", "cpg_e", "uniq_id", "TSS_skew", "strand" ) )
cgi3_m <- gene_info_m |>
  select( c( "chrom",  "gene_s", "gene_e", "uniq_id", "TSS_skew", "strand" ) )

colnames( cgi3_p ) <- c(
    "chrom",
    "start",
    "end",
    "uniq_id",
    "score",
    "strand"
    )
colnames( cgi3_m ) <- c(
    "chrom",
    "start",
    "end",
    "uniq_id",
    "score",
    "strand"
    )

cgi3_p$start <- cgi3_p$start + 100
cgi3_m$end <- cgi3_m$end - 100

cgi3_tab <- rbind(cgi3_p, cgi3_m)
```

```{r}
CnT_CGI_tab <- score_matrix(
      bed = cgi3_tab,
      readsource = paste0( DIR, "GSM5395699_CUT-Tag-BG4.bw" ),
      n = 1,
      ignorestrand = TRUE,
      method = "bi_anch",
      bam_or_bw = "bw"
      )
```

```{r}
colnames(CnT_CGI_tab) = c(colnames(CnT_CGI_tab[,1:6]), "CGIscore")
CnT_CGI_tab$CGIscore <- CnT_CGI_tab$CGIscore * 1000
```

```{r}
CnT_TSS_tab <- as.data.frame(CnT_TSS_tab)
CnT_CGI_tab <- as.data.frame(CnT_CGI_tab)

G4_scores <- cbind(CnT_TSS_tab[1], CnT_TSS_tab[7], CnT_CGI_tab[7])
colnames(G4_scores) <- c("uniq_id", "tss_score", "cgi3_score")
```

```{r}
G4_scores$G4_ratio <- G4_scores$tss_score/G4_scores$cgi3_score
```

So what does the ratio look like?

```{r}
summary(G4_scores$G4_ratio)
```
Oh, should probably add pseudocounts.
```{r}
G4_scores$tss_score <- G4_scores$tss_score + 0.1
G4_scores$cgi3_score <- G4_scores$cgi3_score + 0.1
G4_scores$G4_ratio <- G4_scores$tss_score/G4_scores$cgi3_score
```

```{r}
summary(G4_scores$G4_ratio)
```

```{r}
gene_info <- rbind(gene_info_p, gene_info_m)
parenttab <- merge(gene_info, G4_scores, by = "uniq_id")
```

do I want to filter out the genes that had no signal at either of the two spots?

```{r}
distal <- parenttab |>
  filter(
  simple_skew_class == "Dist" &
  tss_score > 0.11 &
  cgi3_score > 0.11 
  ) 

proximal <- parenttab |>
  filter(
  simple_skew_class == "Prox" &
    tss_score > 0.11 &
    cgi3_score > 0.11 
  ) 
```

Some form of invisible rounding pseudonumber stuff was screwing with the 0, so I had to go up to 0.11 instead of 0.1. 5029 distal and 5574 proximal, so it's not like either class is the one missing data.

```{r}
test = wilcox.test(x = proximal$G4_ratio, y = distal$G4_ratio, paired = FALSE,
            conf.int = TRUE, correct = FALSE)
test
```
It's significant. Less significant than pausing, only passes the 0.05 stringency P, but still, interesting.

```{r}
skew_colors <- c("Proximally skewed" = "blue", "Distally skewed" = "red")
 ggplot() +
  stat_ecdf(geom="step", data=proximal, aes(G4_ratio, color = "Proximally skewed")) +
  stat_ecdf(geom="step", data=distal, aes(G4_ratio, color = "Distally skewed")) +
  mytheme +
  scale_x_log10(n.breaks=6, labels=scales::label_comma()) +
   ggtitle("Proximal/Distal G4 ratio by skew class") +
  scale_color_manual(values = skew_colors) +
  ylab("Cumulative Distribution") +
  annotate("text", x = 5, y = 0.75, label = paste0("p=", signif(test$p.value, digits = 4)))
```
I see. It's technically different, but nowhere near PRO-seq levels of impressive.
