---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

```{r}
library(tidyverse)
library(data.table)
source("~/Script repository/R scripting/Utility_Fns.R")
source( "~/Script repository/R scripting/Matrix_Fns.R" )
```
```{r}
TTseq_timecourse <- fread( "C:/Users/kayle/Box/Vertinolab/McKayla Ford/Projects/R-loops_Pausing/Sequence_based_analysis/Classing_by_Skew/Polenkowski_Timecourse_TTseq/TTseq_timecourse_skewclassed.txt.gz", header=TRUE, drop=c( 2,3,4,5,6,7,8,9,10,15,20,22,23,24,26 ) )
```
#############
Let's quantile by skew at tss and skew at 3' CGI, independent of dist/prox, to see what we see. If we spot something we can always divide things up further. Then could quantile by prox dist difference.

Alright, TSS skew to start with.
```{r}
per0   <- quantile( TTseq_timecourse$TSS_skew, 0   )
per20  <- quantile( TTseq_timecourse$TSS_skew, 0.2 )
per40  <- quantile( TTseq_timecourse$TSS_skew, 0.4 )
per60  <- quantile( TTseq_timecourse$TSS_skew, 0.6 )
per80  <- quantile( TTseq_timecourse$TSS_skew, 0.8 )
per100 <- quantile( TTseq_timecourse$TSS_skew, 1.0 )

per0
per20
per40
per60
per80
per100
```
So now filter.
```{r}
TSS20per  <- TTseq_timecourse[ TSS_skew <= per20 ]
TSS40per  <- TTseq_timecourse[ TSS_skew <= per40 & TSS_skew > per20 ]
TSS60per  <- TTseq_timecourse[ TSS_skew <= per60 & TSS_skew > per40 ]
TSS80per  <- TTseq_timecourse[ TSS_skew <= per80 & TSS_skew > per60 ]
TSS100per <- TTseq_timecourse[ TSS_skew  > per80 ]
```

oh let's check how many dist and prox in each?
```{r}
print( "20th percentile dist vs prox" )
dim( TSS20per[ simple_skew_class == "Dist"] )
dim( TSS20per[ simple_skew_class == "Prox"] )

print( "40th percentile dist vs prox" )
dim( TSS40per[ simple_skew_class == "Dist"] )
dim( TSS40per[ simple_skew_class == "Prox"] )

print( "60th percentile dist vs prox" )
dim( TSS60per[ simple_skew_class == "Dist"] )
dim( TSS60per[ simple_skew_class == "Prox"] )

print( "80th percentile dist vs prox" )
dim( TSS80per[ simple_skew_class == "Dist"] )
dim( TSS80per[ simple_skew_class == "Prox"] )

print( "100th percentile dist vs prox" )
dim( TSS100per[ simple_skew_class == "Dist"] )
dim( TSS100per[ simple_skew_class == "Prox"] )
```


Great. Now I need to pivot and merge. (keep original tab potentially to compare to other tabs)

```{r}
perlist <- list( TSS20per, TSS40per, TSS60per, TSS80per, TSS100per )

nlist <- list( 1:5 )

for ( per in seq_along( perlist ) ) {
    tmptab <- perlist[[per]][, c( 12:412, 414:415 ) ] #removed class used for now
    long_tab <- melt( tmptab, na.rm = TRUE, id.vars = c( "loc", "condition", "time" ) )
    nlist[[per]] <- long_tab[, .(mean_score = mean(value)), by = list(variable, loc, condition, time )]
}

rm( perlist )
```
(keep original IDs potentially to compare to other tabs)
```{r}
TSS20perIDs  <- TSS20per$uniq_id
TSS40perIDs  <- TSS40per$uniq_id
TSS60perIDs  <- TSS60per$uniq_id
TSS80perIDs  <- TSS80per$uniq_id
TSS100perIDs <- TSS100per$uniq_id

rm( TSS20per, TSS40per, TSS60per, TSS80per, TSS100per )
```

```{r}
nlist[[1]]$perc <- "20perc_TSS_skew"
nlist[[2]]$perc <- "40perc_TSS_skew"
nlist[[3]]$perc <- "60perc_TSS_skew"
nlist[[4]]$perc <- "80perc_TSS_skew"
nlist[[5]]$perc <- "100perc_TSS_skew"

TSS_skew_quant <- do.call( rbind, nlist )
```

Alright, need to fix the bin names (. is currently representing -, and everything is prefixed by an X)

```{r}
colnames( TSS_skew_quant )[1] <- "Bins"
TSS_skew_quant$Bins <- sub( "^X", "", TSS_skew_quant$Bins )
TSS_skew_quant$Bins <- sub( "^\\.", "-", TSS_skew_quant$Bins )
TSS_skew_quant$Bins <- as.numeric( TSS_skew_quant$Bins )
TSS_skew_quant$time <- as.character( TSS_skew_quant$time )
```

```{r}
mytheme <- theme(
  panel.background = element_rect( fill = "white" ),
  text = element_text( color = "black", face = "bold", family = "sans" ),
  axis.text = element_text( color = "black" ),
  axis.ticks = element_line( color = "black" ),
  plot.margin = unit( c( 0.25, 0.25, 0.25, 0.25 ), "cm" ),
  plot.title = element_text( vjust = 2 ),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  axis.title.y = element_text( vjust = 0 ),
  axis.title.x = element_text( vjust = 0 ),
  panel.border = element_blank(),
  axis.line = element_line()
)
```

```{r}
geom1_TSS_skew_quant <- TSS_skew_quant |> 
  filter( loc == "TSS" ) |>
  ggplot( aes( x = Bins, y = mean_score, color = perc, linetype = condition)) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_ttseq") +
  facet_wrap(~time) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")
geom1_TSS_skew_quant
```
So it's probably not a raw skew at the TSS thing since the mid percentile is the one with the most obvious waveform, which is also a 50/50 distal proximal region. Same pattern with CGI?

```{r}
geom2_TSS_skew_quant <- TSS_skew_quant |> 
  filter( loc == "CGI" ) |>
  ggplot( aes( x = Bins, y = mean_score, color = perc, linetype = condition)) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_ttseq") +
  facet_wrap(~time) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")
geom2_TSS_skew_quant
```

Yes, same effect.

Okay, what about skew at the 3' edge? (I want to look at CGI length but let's go through this progressively.)


```{r}
per0   <- quantile( TTseq_timecourse$CGI3_skew, 0   )
per20  <- quantile( TTseq_timecourse$CGI3_skew, 0.2 )
per40  <- quantile( TTseq_timecourse$CGI3_skew, 0.4 )
per60  <- quantile( TTseq_timecourse$CGI3_skew, 0.6 )
per80  <- quantile( TTseq_timecourse$CGI3_skew, 0.8 )
per100 <- quantile( TTseq_timecourse$CGI3_skew, 1.0 )

per0
per20
per40
per60
per80
per100
```
So now filter.
```{r}
CGI20per  <- TTseq_timecourse[ CGI3_skew <= per20 ]
CGI40per  <- TTseq_timecourse[ CGI3_skew <= per40 & CGI3_skew > per20 ]
CGI60per  <- TTseq_timecourse[ CGI3_skew <= per60 & CGI3_skew > per40 ]
CGI80per  <- TTseq_timecourse[ CGI3_skew <= per80 & CGI3_skew > per60 ]
CGI100per <- TTseq_timecourse[ CGI3_skew  > per80 ]
```

```{r}
print( "20th percentile dist vs prox" )
dim( CGI20per[ simple_skew_class == "Dist"] )
dim( CGI20per[ simple_skew_class == "Prox"] )

print( "40th percentile dist vs prox" )
dim( CGI40per[ simple_skew_class == "Dist"] )
dim( CGI40per[ simple_skew_class == "Prox"] )

print( "60th percentile dist vs prox" )
dim( CGI60per[ simple_skew_class == "Dist"] )
dim( CGI60per[ simple_skew_class == "Prox"] )

print( "80th percentile dist vs prox" )
dim( CGI80per[ simple_skew_class == "Dist"] )
dim( CGI80per[ simple_skew_class == "Prox"] )

print( "100th percentile dist vs prox" )
dim( CGI100per[ simple_skew_class == "Dist"] )
dim( CGI100per[ simple_skew_class == "Prox"] )
```


```{r}
perlist <- list( CGI20per, CGI40per, CGI60per, CGI80per, CGI100per )

nlist <- list( 1:5 )

for ( per in seq_along( perlist ) ) {
    tmptab <- perlist[[per]][, c( 12:412, 414:415 ) ] #removed class used for now
    long_tab <- melt( tmptab, na.rm = TRUE, id.vars = c( "loc", "condition", "time" ) )
    nlist[[per]] <- long_tab[, .(mean_score = mean(value)), by = list(variable, loc, condition, time )]
}

rm( perlist )
```

```{r}
CGI20perIDs  <- CGI20per$uniq_id
CGI40perIDs  <- CGI40per$uniq_id
CGI60perIDs  <- CGI60per$uniq_id
CGI80perIDs  <- CGI80per$uniq_id
CGI100perIDs <- CGI100per$uniq_id

rm( CGI20per, CGI40per, CGI60per, CGI80per, CGI100per )
```

```{r}
nlist[[1]]$perc <- "20perc_CGI_skew"
nlist[[2]]$perc <- "40perc_CGI_skew"
nlist[[3]]$perc <- "60perc_CGI_skew"
nlist[[4]]$perc <- "80perc_CGI_skew"
nlist[[5]]$perc <- "100perc_CGI_skew"

CGI_skew_quant <- do.call( rbind, nlist )
```

```{r}
colnames( CGI_skew_quant )[1] <- "Bins"
CGI_skew_quant$Bins <- sub( "^X", "", CGI_skew_quant$Bins )
CGI_skew_quant$Bins <- sub( "^\\.", "-", CGI_skew_quant$Bins )
CGI_skew_quant$Bins <- as.numeric( CGI_skew_quant$Bins )
CGI_skew_quant$time <- as.character( CGI_skew_quant$time )
```


```{r}
geom1_CGI_skew_quant <- CGI_skew_quant |> 
  filter( loc == "TSS" ) |>
  ggplot( aes( x = Bins, y = mean_score, color = perc, linetype = condition)) +
      geom_line() +
      mytheme +
      ggtitle(label="cgi_skewed_ttseq") +
  facet_wrap(~time) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")
geom1_CGI_skew_quant
```

```{r}
geom2_CGI_skew_quant <- CGI_skew_quant |> 
  filter( loc == "CGI" ) |>
  ggplot( aes( x = Bins, y = mean_score, color = perc, linetype = condition)) +
      geom_line() +
      mytheme +
      ggtitle(label="cgi_skewed_ttseq") +
  facet_wrap(~time) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")
geom2_CGI_skew_quant
```
Same deal. One last relevant skew one before moving on to distance to CGI edge and TTseq signal. (There is a pattern, but 'it has moderate skew' isn't really an actionable pattern.)

```{r}
TTseq_timecourse$dif <- TTseq_timecourse$TSS_skew - TTseq_timecourse$CGI3_skew
per0   <- quantile( TTseq_timecourse$dif, 0   )
per20  <- quantile( TTseq_timecourse$dif, 0.2 )
per40  <- quantile( TTseq_timecourse$dif, 0.4 )
per60  <- quantile( TTseq_timecourse$dif, 0.6 )
per80  <- quantile( TTseq_timecourse$dif, 0.8 )
per100 <- quantile( TTseq_timecourse$dif, 1.0 )

per0
per20
per40
per60
per80
per100
```
So now filter.
```{r}
dif20per  <- TTseq_timecourse[ dif <= per20 ]
dif40per  <- TTseq_timecourse[ dif <= per40 & dif > per20 ]
dif60per  <- TTseq_timecourse[ dif <= per60 & dif > per40 ]
dif80per  <- TTseq_timecourse[ dif <= per80 & dif > per60 ]
dif100per <- TTseq_timecourse[ dif  > per80 ]
```

```{r}
print( "20th percentile dist vs prox" )
dim( dif20per[ simple_skew_class == "Dist"] )
dim( dif20per[ simple_skew_class == "Prox"] )

print( "40th percentile dist vs prox" )
dim( dif40per[ simple_skew_class == "Dist"] )
dim( dif40per[ simple_skew_class == "Prox"] )

print( "60th percentile dist vs prox" )
dim( dif60per[ simple_skew_class == "Dist"] )
dim( dif60per[ simple_skew_class == "Prox"] )

print( "80th percentile dist vs prox" )
dim( dif80per[ simple_skew_class == "Dist"] )
dim( dif80per[ simple_skew_class == "Prox"] )

print( "100th percentile dist vs prox" )
dim( dif100per[ simple_skew_class == "Dist"] )
dim( dif100per[ simple_skew_class == "Prox"] )
```


```{r}
perlist <- list( dif20per, dif40per, dif60per, dif80per, dif100per )

nlist <- list( 1:5 )

for ( per in seq_along( perlist ) ) {
    tmptab <- perlist[[per]][, c( 12:412, 414:415 ) ] #removed class used for now
    long_tab <- melt( tmptab, na.rm = TRUE, id.vars = c( "loc", "condition", "time" ) )
    nlist[[per]] <- long_tab[, .(mean_score = mean(value)), by = list(variable, loc, condition, time )]
}

rm( perlist )
```

```{r}
dif20perIDs  <- dif20per$uniq_id
dif40perIDs  <- dif40per$uniq_id
dif60perIDs  <- dif60per$uniq_id
dif80perIDs  <- dif80per$uniq_id
dif100perIDs <- dif100per$uniq_id

rm( dif20per, dif40per, dif60per, dif80per, dif100per )
```

```{r}
nlist[[1]]$perc <- "20perc_dif_skew"
nlist[[2]]$perc <- "40perc_dif_skew"
nlist[[3]]$perc <- "60perc_dif_skew"
nlist[[4]]$perc <- "80perc_dif_skew"
nlist[[5]]$perc <- "100perc_dif_skew"

dif_skew_quant <- do.call( rbind, nlist )
```

```{r}
colnames( dif_skew_quant )[1] <- "Bins"
dif_skew_quant$Bins <- sub( "^X", "", dif_skew_quant$Bins )
dif_skew_quant$Bins <- sub( "^\\.", "-", dif_skew_quant$Bins )
dif_skew_quant$Bins <- as.numeric( dif_skew_quant$Bins )
dif_skew_quant$time <- as.character( dif_skew_quant$time )
```


```{r}
geom1_dif_skew_quant <- dif_skew_quant |> 
  filter( loc == "TSS" ) |>
  ggplot( aes( x = Bins, y = mean_score, color = perc, linetype = condition)) +
      geom_line() +
      mytheme +
      ggtitle(label="dif_skewed_ttseq") +
  facet_wrap(~time) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")
geom1_dif_skew_quant
```


```{r}
geom2_dif_skew_quant <- dif_skew_quant |> 
  filter( loc == "CGI" ) |>
  ggplot( aes( x = Bins, y = mean_score, color = perc, linetype = condition)) +
      geom_line() +
      mytheme +
      ggtitle(label="dif_skewed_ttseq") +
  facet_wrap(~time) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")
geom2_dif_skew_quant
```


Hmm. So it's not the strongest difference that shows the waveform, it's the second strongest. Which is still all prox.

```{r}
per0   <- quantile( TTseq_timecourse$TSS_3prime, 0   )
per20  <- quantile( TTseq_timecourse$TSS_3prime, 0.2 )
per40  <- quantile( TTseq_timecourse$TSS_3prime, 0.4 )
per60  <- quantile( TTseq_timecourse$TSS_3prime, 0.6 )
per80  <- quantile( TTseq_timecourse$TSS_3prime, 0.8 )
per100 <- quantile( TTseq_timecourse$TSS_3prime, 1.0 )

per0
per20
per40
per60
per80
per100
```

```{r}
len20per  <- TTseq_timecourse[ TSS_3prime <= per20 ]
len40per  <- TTseq_timecourse[ TSS_3prime <= per40 & TSS_3prime > per20 ]
len60per  <- TTseq_timecourse[ TSS_3prime <= per60 & TSS_3prime > per40 ]
len80per  <- TTseq_timecourse[ TSS_3prime <= per80 & TSS_3prime > per60 ]
len100per <- TTseq_timecourse[ TSS_3prime  > per80 ]
```

```{r}
print( "20th percentile dist vs prox" )
dim( len20per[ simple_skew_class == "Dist"] )
dim( len20per[ simple_skew_class == "Prox"] )

print( "40th percentile dist vs prox" )
dim( len40per[ simple_skew_class == "Dist"] )
dim( len40per[ simple_skew_class == "Prox"] )

print( "60th percentile dist vs prox" )
dim( len60per[ simple_skew_class == "Dist"] )
dim( len60per[ simple_skew_class == "Prox"] )

print( "80th percentile dist vs prox" )
dim( len80per[ simple_skew_class == "Dist"] )
dim( len80per[ simple_skew_class == "Prox"] )

print( "100th percentile dist vs prox" )
dim( len100per[ simple_skew_class == "Dist"] )
dim( len100per[ simple_skew_class == "Prox"] )
```

```{r}
perlist <- list( len20per, len40per, len60per, len80per, len100per )

nlist <- list( 1:5 )

for ( per in seq_along( perlist ) ) {
    tmptab <- perlist[[per]][, c( 12:412, 414:415 ) ] #removed class used for now
    long_tab <- melt( tmptab, na.rm = TRUE, id.vars = c( "loc", "condition", "time" ) )
    nlist[[per]] <- long_tab[, .(mean_score = mean(value)), by = list(variable, loc, condition, time )]
}

rm( perlist )
```

```{r}
len20perIDs  <- len20per$uniq_id
len40perIDs  <- len40per$uniq_id
len60perIDs  <- len60per$uniq_id
len80perIDs  <- len80per$uniq_id
len100perIDs <- len100per$uniq_id

rm( len20per, len40per, len60per, len80per, len100per )
```

```{r}
nlist[[1]]$perc <- "20perc_len"
nlist[[2]]$perc <- "40perc_len"
nlist[[3]]$perc <- "60perc_len"
nlist[[4]]$perc <- "80perc_len"
nlist[[5]]$perc <- "100perc_len"

len_quant <- do.call( rbind, nlist )
```

```{r}
colnames( len_quant )[1] <- "Bins"
len_quant$Bins <- sub( "^X", "", len_quant$Bins )
len_quant$Bins <- sub( "^\\.", "-", len_quant$Bins )
len_quant$Bins <- as.numeric( len_quant$Bins )
len_quant$time <- as.character( len_quant$time )
```


```{r}
geom1_len_quant <- len_quant |> 
  filter( loc == "TSS" ) |>
  ggplot( aes( x = Bins, y = mean_score, color = perc, linetype = condition)) +
      geom_line() +
      mytheme +
      ggtitle(label="len_ttseq") +
  facet_wrap(~time) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")
geom1_len_quant
```

```{r}
geom2_len_quant <- len_quant |> 
  filter( loc == "CGI" ) |>
  ggplot( aes( x = Bins, y = mean_score, color = perc, linetype = condition)) +
      geom_line() +
      mytheme +
      ggtitle(label="len_ttseq") +
  facet_wrap(~time) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")
geom2_len_quant
```
Well, isn't that interesting? There's a lot to unpack there.

Maybe split out by condition so they're easier to see. Then I'm interested in if the skew class is relevant on top of this. (which means I'll need to re-summarize the values.)

```{r}
geom1_len_quant <- len_quant |> 
  filter( loc == "TSS" & condition == "ctrl") |>
  ggplot( aes( x = Bins, y = mean_score, color = perc)) +
      geom_line() +
      mytheme +
      ggtitle(label="len_ttseq") +
  facet_wrap(~time) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")
geom1_len_quant
```
The longest CGI quantile is the one with both the highest peaks (why?) and the downstream pattern. all the other quantiles are shorter than 1kb.

```{r}
geom2_len_quant <- len_quant |> 
  filter( loc == "TSS" & condition == "thoc5") |>
  ggplot( aes( x = Bins, y = mean_score, color = perc)) +
      geom_line() +
      mytheme +
      ggtitle(label="len_ttseq") +
  facet_wrap(~time) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")
geom2_len_quant
```

There is a clear change in behavior at the CpG island edge when you knock Thoc5 out. They're staggered from shortest to longest, and the longest still has a bit of the downstream peaks but it's faded quite a bit.

```{r}
geom3_len_quant <- len_quant |> 
  filter( loc == "CGI" & condition == "ctrl") |>
  ggplot( aes( x = Bins, y = mean_score, color = perc)) +
      geom_line() +
      mytheme +
      ggtitle(label="len_ttseq") +
  facet_wrap(~time) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")
geom3_len_quant
```

This part I don't understand. Why would only the longest CGI have this pattern at the edge? If anything I'd expect bleedthrough of TSS-associated signal in the short ones. Although to be fair, I do need to keep in mind that a lot of the shortest stuff is eliminated in TTseq, and... Well, actually. If tx normally moves at over a KB a minute, maybe the long CGI are the only ones where I'm going to be able to see any effect anyway? Not sure.

```{r}
geom4_len_quant <- len_quant |> 
  filter( loc == "CGI" & condition == "thoc5") |>
  ggplot( aes( x = Bins, y = mean_score, color = perc)) +
      geom_line() +
      mytheme +
      ggtitle(label="len_ttseq") +
  facet_wrap(~time) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")
geom4_len_quant
```
At a bit of a loss for words with this one, TBH. Not sure what to think of it.

With prox/dist:
```{r}
len20per  <- TTseq_timecourse[ TSS_3prime <= per20 ]
len40per  <- TTseq_timecourse[ TSS_3prime <= per40 & TSS_3prime > per20 ]
len60per  <- TTseq_timecourse[ TSS_3prime <= per60 & TSS_3prime > per40 ]
len80per  <- TTseq_timecourse[ TSS_3prime <= per80 & TSS_3prime > per60 ]
len100per <- TTseq_timecourse[ TSS_3prime  > per80 ]
```

```{r}
perlist <- list( len20per, len40per, len60per, len80per, len100per )

nlist <- list( 1:5 )

for ( per in seq_along( perlist ) ) {
    tmptab <- perlist[[per]][, c( 12:415 ) ] 
    long_tab <- melt( tmptab, na.rm = TRUE, id.vars = c( "loc", "condition", "time", "class_used" ) )
    nlist[[per]] <- long_tab[, .(mean_score = mean(value)), by = list(variable, loc, condition, time, class_used )]
}

rm( perlist )
```

```{r}
nlist[[1]]$perc <- "20perc_len"
nlist[[2]]$perc <- "40perc_len"
nlist[[3]]$perc <- "60perc_len"
nlist[[4]]$perc <- "80perc_len"
nlist[[5]]$perc <- "100perc_len"

len_quant <- do.call( rbind, nlist )
```

```{r}
colnames( len_quant )[1] <- "Bins"
len_quant$Bins <- sub( "^X", "", len_quant$Bins )
len_quant$Bins <- sub( "^\\.", "-", len_quant$Bins )
len_quant$Bins <- as.numeric( len_quant$Bins )
len_quant$time <- as.character( len_quant$time )
```

```{r}
geom5_len_quant <- len_quant |> 
  filter( loc == "TSS" & condition == "ctrl" & class_used == "prox") |>
  ggplot( aes( x = Bins, y = mean_score, color = perc)) +
      geom_line() +
      mytheme +
      ggtitle(label="len_ttseq") +
  facet_wrap(~time) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")
geom5_len_quant
```


```{r}
geom6_len_quant <- len_quant |> 
  filter( loc == "TSS" & condition == "ctrl" & class_used == "dist") |>
  ggplot( aes( x = Bins, y = mean_score, color = perc)) +
      geom_line() +
      mytheme +
      ggtitle(label="len_ttseq") +
  facet_wrap(~time) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")
geom6_len_quant
```

```{r}
geom7_len_quant <- len_quant |> 
  filter( loc == "TSS" & condition == "thoc5" & class_used == "prox") |>
  ggplot( aes( x = Bins, y = mean_score, color = perc)) +
      geom_line() +
      mytheme +
      ggtitle(label="len_ttseq") +
  facet_wrap(~time) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")
geom7_len_quant
```

```{r}
geom8_len_quant <- len_quant |> 
  filter( loc == "TSS" & condition == "thoc5" & class_used == "dist") |>
  ggplot( aes( x = Bins, y = mean_score, color = perc)) +
      geom_line() +
      mytheme +
      ggtitle(label="len_ttseq") +
  facet_wrap(~time) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")
geom8_len_quant
```

```{r}
geom9_len_quant <- len_quant |> 
  filter( loc == "CGI" & condition == "ctrl" & class_used == "prox") |>
  ggplot( aes( x = Bins, y = mean_score, color = perc)) +
      geom_line() +
      mytheme +
      ggtitle(label="len_ttseq") +
  facet_wrap(~time) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")
geom9_len_quant
```

```{r}
geom10_len_quant <- len_quant |> 
  filter( loc == "CGI" & condition == "ctrl" & class_used == "dist") |>
  ggplot( aes( x = Bins, y = mean_score, color = perc)) +
      geom_line() +
      mytheme +
      ggtitle(label="len_ttseq") +
  facet_wrap(~time) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")
geom10_len_quant
```

```{r}
geom11_len_quant <- len_quant |> 
  filter( loc == "CGI" & condition == "thoc5" & class_used == "prox") |>
  ggplot( aes( x = Bins, y = mean_score, color = perc)) +
      geom_line() +
      mytheme +
      ggtitle(label="len_ttseq") +
  facet_wrap(~time) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")
geom11_len_quant
```

```{r}
geom12_len_quant <- len_quant |> 
  filter( loc == "CGI" & condition == "thoc5" & class_used == "dist") |>
  ggplot( aes( x = Bins, y = mean_score, color = perc)) +
      geom_line() +
      mytheme +
      ggtitle(label="len_ttseq") +
  facet_wrap(~time) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")
geom12_len_quant
```


