---
title: "A couple more direct comparisons."
output: html_notebook
---

```{r}
library(data.table)
library( tidyverse )
```

```{r}
tab <- fread("C:/Users/kayle/Box/Vertinolab/McKayla Ford/Projects/R-loops_Pausing/Sequence_based_analysis/Classing_by_Skew/Polenkowski_Timecourse_TTseq/TTseq_timecourse_scalednstranded.txt.gz")
```
```{r}
mytheme <- theme(
  panel.background = element_rect( fill = "white" ),
  text = element_text( color = "black", face = "bold", family = "sans" ),
  axis.text = element_text( color = "black" ),
  axis.ticks = element_line( color = "black" ),
  plot.margin = unit( c( 0.25, 0.25, 0.25, 0.25 ), "cm" ),
  plot.title = element_text( vjust = 2 ),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  axis.title.y = element_text( vjust = 0 ),
  axis.title.x = element_text( vjust = 0 ),
  panel.border = element_blank(),
  axis.line = element_line()
)
```

```{r}
tab[, max1:= do.call(pmax, .SD), , .SDcols = c(28:427)]
tab[, maxScore:= max(max1), uniq_id]
tab = tab[maxScore != 0]
tab[,c(28:427)] <- tab[, lapply(.SD, '/', maxScore), , .SDcols = c(28:427)]
```

#and 7

```{r}
len250  <- tab[ TSS_3prime <= 250 ]
len500  <- tab[ TSS_3prime <= 500 & TSS_3prime > 250 ]
len750  <- tab[ TSS_3prime <= 750 & TSS_3prime > 500 ]
len1000  <- tab[ TSS_3prime <= 1000 & TSS_3prime > 750 ]
len1250  <- tab[ TSS_3prime <= 1250 & TSS_3prime > 1000 ]
len1500 <- tab[ TSS_3prime <= 1500 & TSS_3prime > 1250 ]
lenbig <- tab[ TSS_3prime  > 1500 ]
```

```{r}
length(unique(len250$uniq_id))
length(unique(len500$uniq_id))
length(unique(len750$uniq_id))
length(unique(len1000$uniq_id))
length(unique(len1250$uniq_id))
length(unique(len1500$uniq_id))
length(unique(lenbig$uniq_id))
```

```{r}
lenlist <- list( len250, len500, len750, len1000, len1250, len1500, lenbig )

nlist <- list( 1:7 )

for ( per in seq_along( lenlist ) ) {
    tmptab <- lenlist[[per]][, c( 21, 22, 28:429, 431 ) ] 
    sum_tab <- tmptab[, lapply(.SD, mean), by = list(loc, condition, timepoint, senseanti, simple_skew_class )]
    nlist[[per]] <- melt( sum_tab, na.rm = TRUE, id.vars = c( "loc", "condition", "timepoint", "senseanti", "simple_skew_class" ) )
}

rm( lenlist )
```

```{r}
nlist[[1]]$perc <- "len250"
nlist[[2]]$perc <- "len500"
nlist[[3]]$perc <- "len750"
nlist[[4]]$perc <- "len1000"
nlist[[5]]$perc <- "len1250"
nlist[[6]]$perc <- "len1500"
nlist[[7]]$perc <- "lenbig"

len_fixed_7_ds <- do.call( rbind, nlist )
```

```{r}
len_fixed_7_ds$Bins <- (as.numeric( len_fixed_7_ds$variable )  - 100) * 10
len_fixed_7_ds[loc == "CGI5"]$Bins <- len_fixed_7_ds[loc == "CGI5"]$Bins - 2000
len_fixed_7_ds$mean_score <- len_fixed_7_ds$value
```

###################################################

Okay, let's do sense, 10 minutes, len500, include both prox and dist + sense and AS but due to scale diff with THOC5ko put that on a separate graph.
```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "ctrl" & perc == "len500" & timepoint == "min10") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_10_min_ctrl_250_500_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```
20 min
```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "ctrl" & perc == "len500" & timepoint == "min20") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_20_min_ctrl_250_500_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```

```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "ctrl" & perc == "len500" & timepoint == "min30") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_30_min_ctrl_250_500_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```

```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "ctrl" & perc == "len500" & timepoint == "min40") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_40_min_ctrl_250_500_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")+
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```





######################
thoc5ko
```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "thoc5ko" & perc == "len500" & timepoint == "min10") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_10_min_thoc5ko_250_500_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")+
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```
20 min
```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "thoc5ko" & perc == "len500" & timepoint == "min20") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_20_min_thoc5ko_250_500_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")+
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```

```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "thoc5ko" & perc == "len500" & timepoint == "min30") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_30_min_thoc5ko_250_500_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")+
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```

```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "thoc5ko" & perc == "len500" & timepoint == "min40") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_40_min_thoc5ko_250_500_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")+
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```


###########################
```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "ctrl" & perc == "len750" & timepoint == "min10") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_10_min_ctrl_500_750_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")+
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```
20 min
```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "ctrl" & perc == "len750" & timepoint == "min20") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_20_min_ctrl_500_750_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")+
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```

```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "ctrl" & perc == "len750" & timepoint == "min30") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_30_min_ctrl_500_750_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")+
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```

```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "ctrl" & perc == "len750" & timepoint == "min40") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_40_min_ctrl_500_750_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")+
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```

################
thoc5ko
```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "thoc5ko" & perc == "len750" & timepoint == "min10") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_10_min_thoc5ko_500_750_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")+
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```
20 min
```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "thoc5ko" & perc == "len750" & timepoint == "min20") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_20_min_thoc5ko_500_750_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")+
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```

```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "thoc5ko" & perc == "len750" & timepoint == "min30") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_30_min_thoc5ko_500_750_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")+
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```

```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "thoc5ko" & perc == "len750" & timepoint == "min40") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_40_min_thoc5ko_500_750_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")+
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```

####################

```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "ctrl" & perc == "len1000" & timepoint == "min10") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_10_min_ctrl_750_1000_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")+
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```
20 min
```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "ctrl" & perc == "len1000" & timepoint == "min20") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_20_min_ctrl_750_1000_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")+
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```

```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "ctrl" & perc == "len1000" & timepoint == "min30") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_30_min_ctrl_750_1000_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")+
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```

```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "ctrl" & perc == "len1000" & timepoint == "min40") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_40_min_ctrl_750_1000_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")+
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```





######################
thoc5ko
```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "thoc5ko" & perc == "len1000" & timepoint == "min10") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_10_min_thoc5ko_750_1000_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")+
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```
20 min
```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "thoc5ko" & perc == "len1000" & timepoint == "min20") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_20_min_thoc5ko_750_1000_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")+
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```

```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "thoc5ko" & perc == "len1000" & timepoint == "min30") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_30_min_thoc5ko_750_1000_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")+
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```

```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "TSS" & condition == "thoc5ko" & perc == "len1000" & timepoint == "min40") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_40_min_thoc5ko_750_1000_len") +
      xlab(label="Distance from TSS (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black")+
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```

Since most of the upstream edges are within ~600 bp, for the upstream fixed let's just do 250, 500, 750, 1000, and 1000+.

```{r}
len250  <- tab[ prime5_TSS <= 250 ]
len500  <- tab[ prime5_TSS <= 500 & prime5_TSS > 250 ]
len750  <- tab[ prime5_TSS <= 750 & prime5_TSS > 500 ]
len1000  <- tab[ prime5_TSS <= 1000 & prime5_TSS > 750 ]
lenbig <- tab[ prime5_TSS  > 1000 ]
```

```{r}
lenlist <- list( len250, len500, len750, len1000, lenbig )

nlist <- list( 1:5 )

for ( per in seq_along( lenlist ) ) {
    tmptab <- lenlist[[per]][, c( 21, 22, 28:429, 431 ) ] 
    sum_tab <- tmptab[, lapply(.SD, mean), by = list(loc, condition, timepoint, senseanti, simple_skew_class )]
    nlist[[per]] <- melt( sum_tab, na.rm = TRUE, id.vars = c( "loc", "condition", "timepoint", "senseanti", "simple_skew_class" ) )
}

rm( lenlist )
```

```{r}
nlist[[1]]$perc <- "len250"
nlist[[2]]$perc <- "len500"
nlist[[3]]$perc <- "len750"
nlist[[4]]$perc <- "len1000"
nlist[[5]]$perc <- "lenlong"

len_fixed_5_us <- do.call( rbind, nlist )
```

```{r}
len_fixed_5_us$Bins <- (as.numeric( len_fixed_5_us$variable )  - 100) * 10
len_fixed_5_us[loc == "CGI5"]$Bins <- len_fixed_5_us[loc == "CGI5"]$Bins - 2000
len_fixed_5_us$mean_score <- len_fixed_5_us$value
```

```{r}
geom <- len_fixed_5_us |> 
  filter( loc == "TSS" & senseanti == "antisense" & simple_skew_class == "Dist" & condition == "thoc5ko") |>
  ggplot( aes( x = Bins, y = mean_score, color = perc )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_ttseq_antisense_thoc5ko_dist") +
      xlab(label="Distance from TSS (BP)") +
  facet_wrap(~timepoint) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 100, by=100), limits=c(-1000, 100))
geom
```

CGI edge?
```{r}
geom <- len_fixed_7_ds |> 
  filter( loc == "CGI3" & condition == "ctrl" & perc == "len500" & timepoint == "min10") |>
  ggplot( aes( x = Bins, y = mean_score, color = simple_skew_class, linetype = senseanti )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_10_min_ctrl_250_500_len") +
      xlab(label="Distance from CGI3 (BP)") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = 600, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 1250, by=100), limits=c(-1000, 1250))
geom
```

I don't see as much of a defined peak, to be honest. Maybe 600/2 to be equivalent to TSS region.

```{r}
geom <- len_fixed_5_us |> 
  filter( loc == "CGI5" & senseanti == "antisense" & simple_skew_class == "Dist" & condition == "thoc5ko") |>
  ggplot( aes( x = Bins, y = mean_score, color = perc )) +
      geom_line() +
      mytheme +
      ggtitle(label="tss_ttseq_antisense_thoc5ko_dist") +
      xlab(label="Distance from CGI5 (BP)") +
  facet_wrap(~timepoint) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = 300, linetype = "dashed", color = "Black") +
    geom_vline(xintercept = -300, linetype = "dashed", color = "Black") +
  scale_x_continuous( breaks=seq(-1000, 100, by=100), limits=c(-1000, 100))
geom
```
Okay, the -300 seems okay for the CGI edge situation though.


idea that's probably a bad one... If treated independently, what is the 100 bp skew maxima region in the first couple kb of each gene? Is that a better predictor of TT-seq maxima than CGI edge is?


